---
title: "tidycensus-collab"
format: html
editor: visual
---

```         
```

Interesting. With each point being a census tract, and a correlation coefficient (*R*) of -0.39, what is the relationship between poverty and education at the tract level in Honolulu County?

------------------------------------------------------------------------

## Challenge Time!!

This could be a useful reference: <https://walker-data.com/census-r/index.html>

Replace family poverty with another variable and:

1.  Map it
2.  Show the variable over time
3.  Show the variable's relationship with education (or another variable of your choosing)
4.  Describe what you found

Directions:

1.  One person save as tidycensus_intro-collab.Rmd, commit & push. The other person pull!

2.  Take turns! Who will do what? Be careful not to overwrite one another.

    -   I will be looking for at least 4 exchanges

3.  Paste your challenge answers below

REMEMBER! [Pull]{.underline} before working in the `-collab.qmd` file. [Save, Commit, and Push]{.underline} your changes when you are done. The next person should [Pull]{.underline} before working, and so on.

### Import Data

Investigating (insert variable here) on Oahu at the census tract level.

```{r}
# get the data
texas_poverty <- get_acs(
  geography = "tract",
  variables = c(percent_poverty = "DP03_0119P"),
  state = "TX",
  #county = "Dallas",
  geometry = TRUE,
  output = "wide" )
#  year = 2023) %>% 
#  dplyr::filter(GEOID != "15003981200" & GEOID !="15003981900")
```

### Mapping

```{r}
# MAP IT
texas_poverty_map <- ggplot(texas_poverty) +
  geom_sf_interactive(
    aes(
      fill = percent_povertyE,
      tooltip = paste(NAME, ": ", percent_povertyE, "%"),
      data_id = NAME)) +
  scale_fill_viridis_c(option = "inferno") +
  theme_void() 

girafe(ggobj = texas_poverty_map, width = 700, height = 400)
```

### Time Series

```{r}

```

### Scatter plot

```{r}

```
